English-Chinese Translation Machine Based on Sequence to Sequence Network

### 2022-11-23 ML1/paper.tex
11-23

% Write abstract here
\begin{abstract}
This report is about first experience in machine learning. We explained how to build a anaconda environment to launch python scripts. In second part, three deep learning models to face detection was been used. Consequently, statistics of this experience was been showed and in the final, we have attached some face detection results.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is a important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} used convolutional neural network (CNN). This experience use method raised by \cite{8080244} to detection faces in photos.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network

\section{Experiments}
\subsection{Dataset}
Test dataset includes handurds of photos and all of them has at least one people.

\subsection{Result}
We used the parameters archive files provided by Github repository to test truly effect of these three models. Program scripts load images from test photos folder, annotated them by face in and conveted annotated images into result folder. Whole test processing cost about 9 sec. by a laptop. We picked two of them to explain the effects of face detection, both of them have at least two person in it. First photo like Fig.\ref{fig:13869_raw} includes two persons, while one of them was back to the camera and another was frontal. So only face-to-camera one's face was been annotated by program like Fig.\ref{fig:13869}. Another photo that three person in was been annotated exactly with all the people like Fig.\ref{fig:13692}

@@

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13692.jpg}
		% Create a subtitle for the figure.
		\caption{three person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692_raw}
		\end{center}
	\end{figure}
	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13869.jpg}
		% Create a subtitle for the figure.
		\caption{two person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869_raw}
		\end{center}
	\end{figure}

\section{Conclusion}
	Multi-task convolutional neural network can play a crucial role in face detection.

>>>>

% Write abstract here
\begin{abstract}
This report is about first experience in machine learning. We explained how to build a anaconda environment to launch python scripts. In second part, three deep learning models to face detection was been used. Consequently, statistics of this experience was been showed and in the final, we have attached some face detection results to reveal utility of models.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is an important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} used convolutional neural network (CNN). This experience use method raised by \cite{8080244} to detection faces in photos.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network to detect faces from images. Our experience used this method to handle photos in dataset. Whole Model includes three sub-models which are Proposal Network(P-Net), Refine Network(R-Net) and Output Network(O-Net). Each of these sub-models has its assignment respectively, in which generating bounding boxes for P-Net, removing no-face bounding boxes for R-Net while add landmark in photos for O-Net.

The learning objective is formulated as a two-class classification problem. For each sample $x_{i}$, this method uses the cross-entropy loss as equation.\ref{loss1}, where $p_{i}$ is the probability produced by the network that indicates a sample being a face.

\begin{equation}
    L_{i}^{det}=-(y_{i}^{det}log(p_{i})+(1-y_{i}^{det})(1-log(p_{i})) )\label{loss1}
\end{equation}

For each candidate window, we  predict the offset between it and the nearest ground truth (i.e., the bounding boxes’ left top, height, and width). The learning objective is formulated as a regression problem, and this method employed the Euclidean loss for each sample $x_{i}$ as equation.\ref{eq2}.
\begin{equation}
    L_{i}^{box}=\Vert \hat{y}_{i}^{box}-y_{i}^{box} \Vert_2^{2} \label{eq2}
\end{equation}

\section{Experiments}
\subsection{Dataset}
Training dataset includes more than ten thousand photos and all of them has at least one people facing to camera. Test dataset includes more than one thousand photos. In experience's testing procession, all images in test dataset were been marked by O-Net.

\subsection{Result}
We used the parameters archive files provided by Github repository to test truly effect of these three models. Program scripts load images from test photos folder, annotated them by face in and converted annotated images into result folder. Whole test processing cost about 9 sec. by a laptop with a GPU as NVIDIA GTX 950M. Time costing result revealing printscreens are Fig.\ref{fig:cost}.  We picked two of them to explain the effects of face detection, both of them have at least two person in it. First photo like Fig.\ref{fig:13869_raw} includes two persons, while one of them was back to the camera and another was frontal. So only face-to-camera one's face was been annotated by program like Fig.\ref{fig:13869}. Another photo that three person in was been annotated exactly with all the people like Fig.\ref{fig:13692}

@@

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13692.jpg}
		% Create a subtitle for the figure.
		\caption{three person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692_raw}
		\end{center}
	\end{figure}

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13869.jpg}
		% Create a subtitle for the figure.
		\caption{two person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869_raw}
		\end{center}
	\end{figure}
	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/cost.png}
		% Create a subtitle for the figure.
		\caption{cost time}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:cost}
		\end{center}
	\end{figure}

\section{Conclusion}
	Multi-task convolutional neural network can play a crucial role in face detection. In this experience, we use three models to detect faces in photos. Due to lots parameter in models, it cost a long time to train all detection model in laptop. In training processing, we used late version pytorch to train models so python interpreter gave a warning in \textit{torch.nn}.

### 2022-11-23 ML2/paper.tex
11-23

% Write abstract here
\begin{abstract}
This report is about first experience in machine learning. We explained how to build a anaconda environment to launch python scripts. In second part, three deep learning models to face detection was been used. Consequently, statistics of this experience was been showed and in the final, we have attached some face detection results.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{L}{anguages} are carriers of information transmission. Many kinds of languages are being using among whole world. One of research target in natural language processing field is how translate a language into another language accurately. With the inspiration from classic sequence-to-sequence machine translation models like \cite{1703.01619} and attention mechanism added machine learning language translation models like. \cite{1706.03762}.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network to detect faces from images. Our experience used this method.

\section{Experiments}
\subsection{Dataset}
In this experience, we used English-Chinese translation dataset to train the model.

\subsection{Result}
We used the parameters archive files provided by Github repository to test truly effect of these three models. Program scripts load images from test photos folder, annotated them by face in and conveted annotated images into result folder. Whole test processing cost about 9 sec. by a laptop. We picked two of them to explain the effects of face detection, both of them have at least two person in it. First photo like Fig.\ref{fig:13869_raw} includes two persons, while one of them was back to the camera and another was frontal. So only face-to-camera one's face was been annotated by program like Fig.\ref{fig:13869}. Another photo that three person in was been annotated exactly with all the people like Fig.\ref{fig:13692}

>>>>

% Write abstract here
\begin{abstract}
This report is about second experience in machine learning. We explained how to build a anaconda environment to launch python scripts to train a model in machine translation. In second part, we have pre-processed raw training data and trained a Encoder-Decoder model to translate English into Chinese. Consequently, statistics of this experience was been attached.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{L}{anguages} are carriers of information transmission. Many kinds of languages are being using among whole world. One of research target in natural language processing field is how translate a language into another language accurately. With the inspiration from classic sequence-to-sequence machine translation models like \cite{1703.01619} and attention mechanism added machine learning language translation models like \cite{10.5555/3295222.3295349}. The first time that Encoder-Decoder likes model used in machine translation was \cite{cho-etal-2014-learning}. In this method, Gated Recurrent Unit (GRU) was added into model to catch history information between tokens. Another model used Encoder-Decoder model to translate natural languages is \cite{10.5555/2969033.2969173} while it used Long Short Term Memory (LSTM) to learn implicit connection information from sequence.

% Main Part
\section{Methods and Theory}

\section{Experiments}
\subsection{Dataset}
In this experience, we used English-Chinese translation dataset to train the model. In this case, this experience's model can convert English to Chinese and convert Chinese to English.

\subsection{Result}

In training processing, the input sentence is passed to the encoder and each output and the final hidden state are recorded. The <SOS> token is fed as the first input to the decoder and the final hidden state of the encoder as its first hidden state.
